MS Depression Paper, post replication, started 2022 09 21

### 2023-10-21 scripts/msdepression_n380_BP_r1_script.Rmd
Create msdepression_n380_BP_r1_script.Rmd

    -Main effect of network Dep > Nondep (Estimate = 0.09, 95% CI 0.070-0.10, P <0.001)
    -Main effects of diagnosis MS+Depression > MS-Depression (Estimate = 0.05, 95% CI 0.001-0.095, P= 0.046)
    -Main effect of interaction (Estimate = 0.018, 95% CI 0.00 - 0.030, P=0.060)

@@

#Final data: 
#Main effect of network Dep > Nondep (Estimate = 0.09, 95% CI 0.070-0.10, P <0.001)
#Main effects of diagnosis MS+Depression > MS-Depression (Estimate = 0.05, 95% CI 0.001-0.095, P= 0.046)
#Main effect of interaction (Estimate = 0.018, 95% CI 0.00 - 0.030, P=0.060)

>>>>

    -Main effect of network Dep > Nondep (Estimate = 0.09, 95% CI 0.08-0.11, P <0.001)
    -Main effects of diagnosis MS+Depression > MS-Depression (Estimate = 0.05, 95% CI 0.001-0.095, P= 0.046)
    -Main effect of interaction (Estimate = 0.018, 95% CI 0.00 - 0.030, P=0.060)

@@

#Final data: 
#Main effect of network Dep > Nondep (Estimate = 0.09, 95% CI 0.08-0.11, P <0.001)
#Main effects of diagnosis MS+Depression > MS-Depression (Estimate = 0.05, 95% CI 0.001-0.095, P= 0.046)
#Main effect of interaction (Estimate = 0.018, 95% CI 0.00 - 0.030, P=0.060)
